---
title: "Automated report"
subtitle: "Predictive performance of spatio-temporal model(s)"
author:
  - name: Julie Vercelloni
    corresponding: true
    email: j.vercelloni@aims.gov.au
    affiliations:
      - ref: aimsqld
      - ref: qut
  - name: Murray Logan
    email: m.logan@aims.gov.au
    affiliations:
      - ref: aimsqld
affiliations:
  - id: aimsqld
    name: Australian Institute of Marine Science, Cape Cleveland, Queensland 4810
  - id: qut
    name: Centre for Data Science, Queensland University of Technology, Brisbane, Queensland 4000
engine: knitr
format:
  html:
    toc: true
    toc-location: left
    title-block-banner: true
    toc-depth: 3
    highlight-style: atom-one
    embed-resources: true
    theme:
      light: flatly
      dark: darkly
    code-overflow: wrap
    code-fold: false
    number-sections: true
    number-depth: 2
    shift-heading-level-by: -1
    crossref:
      lst-title: Code listing
    fig-align: center
    text-align: center
    acm-html: default
css: styles.css
execute: 
  message: false
  warning: false
  cache: true
editor:
  markdown:
    wrap: 72
---

```{r, chunkOpts, echo = FALSE}
knitr::opts_chunk$set(cache = TRUE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "..")
```

::: {.callout-caution collapse="true"}
I am an automated report that reads results from the home folder. The number of simulations and models are selected by the user.   
:::
### Simulation summary {.unnumbered}

```{r}
#| include: true
#| echo: false
#| eval: true
#| cache: false

rm(list=ls())

# Source packages and functions 
path <- "../"
source(paste0(path,"R/packages.R"))
source(paste0(path,"R/functions.R"))
```

```{r}
#| include: true
#| echo: false
#| eval: true
#
# Grep names and locations of simulations in the home folder
all_dirs <- list.dirs(path, full.names = FALSE, recursive = FALSE)
exclude_patterns <- c("R", "scripts", ".git")
included_dirs <- all_dirs[!sapply(all_dirs, function(dir) any(grepl(paste(exclude_patterns, collapse = "|"), dir)))] 

# Grep the models that ran for each simulations 
file <- list.files(str_glue("{path}{included_dirs}/model_outputs/full_run"),
    full.names = TRUE
  )

# Extract second term and last term without .Rdata
table_data <- data.frame(
  simulation = map_chr(str_split(file, "/"), 2),               
  model = str_remove(str_remove(file, "^.*/"), "\\.Rdata$")) %>%
  dplyr::group_by(simulation) %>%
  dplyr::summarize(
    number_of_models = n(),                            
    model_names = toString(unique(model))  
  )

# Assign figure path
assign("FIGURES_PATH", "/report/extra/", envir = .GlobalEnv)
```

There are `r length(included_dirs)` simulations in the home folder.  

```{r}
#| label: tbl-mod
#| eval: true
#| echo: false
#| tbl-cap: Number of models per simulation. 
knitr::kable(table_data)
```

::: {.callout-note appearance="simple" icon=false collapse="true"}
#### Predictive performance 

A total of four predictive measures are reported: 

* 95% coverage interval (Cvg) - evaluates how often predictions include true observations, with the goal of capturing the true values 95% of the time. 
* 95% interval score (IS) - rewards prediction intervals that include the true observations (accuracy) and penalizes those that are too narrow or too wide (precision).  
* Root-mean-squared prediction error (RMSPE) - how far off model predictions are from true observations without considering for uncertainty.
* Continuous Ranked Probability Score (CRPS) - represents the quality of the predictions over the entire predictive probability distribution penalizing predictions that are inaccurate, imprecise or overconfident.  

These predictive measures give a single number with low scores representing better performances. In addition, the time (in min) associated with the computation of model fit is also reported in the below figure. 

::: {.panel-tabset collapse="true"}

#### By model 
```{r, fig.width=15, fig.height=15}
#| label: fig-mod
#| eval: true
#| echo: false
#| fig-cap: Model predictive performances for each model. 

# level 1 = plots from the home folder 
print_attr_plots_level1(
  list_folders = included_dirs,
  name_plot = "viz_perf_model_"
)

```
:::

::: {.panel-tabset collapse="true"}

#### By simulation 

```{r, fig.width=15, fig.height=15}
#| label: fig-sim
#| eval: true
#| echo: false
#| fig-cap: Model predictive performances for each simulation. 

# level 2 = plots from the simulation folders and put them together, subtitle = add model name on plots if needed   
fig_perf <- print_attr_plots_level2(
  list_folders = included_dirs,
  name_plot = "viz_perf.png"
)

fig_perf
```  
:::

:::

::: {.callout-note appearance="simple" icon=false collapse="true"}
#### Model fit 

```{r, fig.width=15, fig.height=15}
#| label: fig-fit
#| eval: true
#| echo: false
#| fig-cap: Predictions versus true values.  

# level 2 = plots from the simulation folders and put them together
print_attr_plots_level2(
  list_folders = included_dirs,
  name_plot = "check_true.png"
)
``` 
:::

::: {.callout-note appearance="simple" icon=false collapse="true"}
#### Covariate contributions 
:::

### Simulation details {.unnumbered}

::: {.callout-note appearance="simple" icon=false collapse="true"}
#### Regional trends 

```{r, fig.width=15, fig.height=15}
#| results: asis
#| panel: tabset

# level 3 = plots from the simulation folders and put them into new tabs, subtitle = add model name, plot labels = automatic labels  
fig_region <- purrr::walk(
  included_dirs, 
  ~ print_attr_plots_level3(
    list_folders = .x, 
    name_plot = "pred_broad", 
    subtitle = TRUE, 
    plot_labels = TRUE, 
    label = "Regional trend in",
    n_cols = 2
  )
)

fig_region
```
:::

::: {.callout-note appearance="simple" icon=false collapse="true"}
#### Model prediction

```{r, fig.width=15, fig.height=15}
#| results: asis
#| panel: tabset

# level 3 = plots from the simulation folders and put them into new tabs, subtitle = add model name, plot labels = automatic labels  
fig_pred <- purrr::walk(
  included_dirs, 
  ~ print_attr_plots_level3(
    list_folders = .x, 
    name_plot = "pred[A-Za-z0-9]+", 
    subtitle = TRUE, 
    plot_labels = TRUE, 
    label = "Predictions in",
    n_cols = 2
  )
)

fig_pred
```
:::

::: {.callout-note appearance="simple" icon=false collapse="true"}
#### Model uncertainty

```{r, fig.width=15, fig.height=15}
#| results: asis
#| panel: tabset

# level 3 = plots from the simulation folders and put them into new tabs, subtitle = add model name, plot labels = automatic labels  
fig_pred_unc <- purrr::walk(
  included_dirs, 
  ~ print_attr_plots_level3(
    list_folders = .x, 
    name_plot = "pred_unc[A-Za-z0-9]+", 
    subtitle = TRUE, 
    plot_labels = TRUE, 
    label = "Prediction uncertainty in",
    n_cols = 2
  )
)

fig_pred_unc
```
:::

::: {.callout-note appearance="simple" icon=false collapse="true"}
#### Trends at observed locations

```{r, fig.width=15, fig.height=15}
#| results: asis
#| panel: tabset

# level 3 = plots from the simulation folders and put them into new tabs, subtitle = add model name, plot labels = automatic labels  
fig_data <- purrr::walk(
  included_dirs, 
  ~ print_attr_plots_level3(
    list_folders = .x, 
    name_plot = "pred_traj_tier_data[A-Za-z0-9]+", 
    subtitle = TRUE, 
    plot_labels = TRUE, 
    label = "Predicted trends at observed locations in",
    n_cols = 2
  )
)

fig_data
```
:::

::: {.callout-note appearance="simple" icon=false collapse="true"}
#### Trends at unobserved locations

```{r, fig.width=15, fig.height=15}
#| results: asis
#| panel: tabset

# level 3 = plots from the simulation folders and put them into new tabs, subtitle = add model name, plot labels = automatic labels  
fig_no_data <- purrr::walk(
  included_dirs, 
  ~ print_attr_plots_level3(
    list_folders = .x, 
    name_plot = "pred_traj_tier_no_data[A-Za-z0-9]+", 
    subtitle = TRUE, 
    plot_labels = TRUE, 
    label = "Predicted trends at unobserved locations in",
    n_cols = 2
  )
)

fig_no_data
```
:::

::: {.callout-note appearance="simple" icon=false collapse="true"}
#### Simulated coral data 

```{r, fig.width=15, fig.height=15}
#| results: asis
#| panel: tabset

# level 3 = plots from the simulation folders and put them into new tabs, subtitle = add model name, plot labels = automatic labels  
fig_synthos <- purrr::walk(
  included_dirs, 
  ~ print_attr_plots_level3(
    list_folders = .x, 
    name_plot = "trend_data_fixed", 
    subtitle = TRUE, 
    plot_labels = TRUE, 
    label = "Synthos data in",
    n_cols = 1
  )
)

fig_synthos
```
:::

::: {.callout-note appearance="simple" icon=false collapse="true"}
#### Disturbance data 

::: {.panel-tabset collapse="true"}

#### Cyclone data  
```{r, fig.width=15, fig.height=15}
#| results: asis
#| panel: tabset

# level 3 = plots from the simulation folders and put them into new tabs, subtitle = add model name, plot labels = automatic labels  
fig_cyclone <- purrr::walk(
  included_dirs, 
  ~ print_attr_plots_level3(
    list_folders = .x, 
    name_plot = "cyclone", 
    subtitle = FALSE, 
    plot_labels = TRUE, 
    label = "Cyclone data in",
    n_cols = 1
  )
)

fig_cyclone
```

:::

::: {.panel-tabset collapse="true"}

#### DHW data 

```{r, fig.width=15, fig.height=15}
#| results: asis
#| panel: tabset

# level 3 = plots from the simulation folders and put them into new tabs, subtitle = add model name, plot labels = automatic labels  
fig_dhw <- purrr::walk(
  included_dirs, 
  ~ print_attr_plots_level3(
    list_folders = .x, 
    name_plot = "dhw", 
    subtitle = FALSE, 
    plot_labels = TRUE, 
    label = "DHW data in",
    n_cols = 1
  )
)

fig_dhw
``` 
:::

::: {.panel-tabset collapse="true"}

#### Other data  
```{r, fig.width=15, fig.height=15}
#| results: asis
#| panel: tabset

# level 3 = plots from the simulation folders and put them into new tabs, subtitle = add model name, plot labels = automatic labels  
fig_ot <- purrr::walk(
  included_dirs, 
  ~ print_attr_plots_level3(
    list_folders = .x, 
    name_plot = "other", 
    subtitle = FALSE, 
    plot_labels = TRUE, 
    label = "Other disturbance data in",
    n_cols = 1
  )
)

fig_ot
``` 
:::

:::

::: {.callout-note appearance="simple" icon=false collapse="true"}
#### Configuration  

```{r}
#| results: asis
#| panel: tabset

# Grep the models that ran for each simulations 
files <- list.files(
  str_glue("{path}{included_dirs}"), 
  pattern = "\\.RData$", 
  full.names = TRUE
)

config_tables <- map(files, load_and_extract)  

combined_tables <- map(c("config_sp", "config_large", "config_fine", "config_pt"), ~ {
  map_dfr(config_tables, .x) # Combine rows from the same named table
})

# Name the resulting tables
names(combined_tables) <- c("spatial parameters", "large-scale parameters", "fine-scale parameters", "sampling design configuration")

purrr::walk2(names(combined_tables), combined_tables, ~ {
  # Add a markdown heading and caption
  cat("####", .x, "\n\n")  
  # Create a dynamic table label in Quarto format
  div_label <- paste0("#tbl-", gsub(" ", "", .x))  # Remove spaces from table names
  caption_text <- paste("Configuration of", .x)
  print(kable(head(.y)))
  cat(paste0(":", caption_text, " {", div_label, "}"), "\n\n")
})

```
:::
